Anomalous waves triggered by abrupt depth changes: experimental measurements and deterministic-statistical truncated KdV theory

### 2019-10-08 paper2_JNLS/paper.tex
NM

Briefly, consider the parameter $\lamfac$, the number of characteristic wavelengths in the physical domain. We require $\lamfac \le \Lambda$, so that the mode $\uhat_{\lamfac}$, corresponding to the characteristic wavelength $\lam$ in the experiments, is resolved in the truncated dynamical system. If $\lamfac = \Lambda$, then $\lam$ corresponds to the smallest resolved wavelength. Often, we will choose an intermediate value such as $\lamfac = \Lambda/2$ or $\Lambda/4$, so that the truncated system \eqref{TKdV} resolves scales that are both bigger and smaller than the characteristic value $\lam$.

@@

	Since the inverse temperature, $\theta$, is a key modeling parameter, it would be highly desirable to normalize the system such that its value does not depend sensitively on the truncation number, $\Lambda$, as $\Lambda$ grows large. That way, $\theta$ can be interpreted as a real physical parameter that can be linked to the experiments and whose value does not depend sensitively on where one chooses to truncate the system. The one modeling parameter that is left to be set is $\lamfac$, which represents the number of characteristic wavelengths in the periodic domain. In what follows, we will determine reasonable constraints on $\lamfac$ that allow $\theta$ to be asymptotically independent of $\Lambda$.

@@

	Importantly, \eqref{HtwoExpect} shows that the expected value of $\Htwo$ grows like $\Lambda^2$, which appears to be problematic for obtaining independence as $\Lambda \to \infty$. However, $\Htwo$ enters $\Ham$ in product with the coefficient $C_2$, which itself scales as $C_2 \sim \lamfac^{-2}$. Hence, to obtain asymptotic independence of $\Lambda$, it is necessary that $\lamfac$ grow proportionally to $\Lambda$, as was already argued on physical grounds in Section \ref{tKdVSec}. 
Thus, any of the choices $\lamfac = \Lambda, \Lambda/2, \Lambda/4$, discussed in that section would be valid.

\vsp{5}

The parameter $\lamfac$ can be chosen in a sensible way by simply selecting an intermediate value between 1 and $\Lambda$, so that some scales both larger than and smaller than the characteristic wavelength $\lam$ are resolved. Hence, we will simply chose $\lamfac = \Lambda/2$ throughout, so that on a log-scale, the characteristic wavelength lies directly in the middle of the resolved wavelengths.

>>>>

Briefly, consider the parameter $\lamfac$, the number of characteristic wavelengths in the physical domain. We require $\lamfac \le \Lambda$, so that the mode $\uhat_{\lamfac}$, corresponding to the characteristic wavelength $\lam$ in the experiments, is resolved in the truncated dynamical system. If $\lamfac = \Lambda$, then $\lam$ corresponds to the smallest resolved wavelength. In contrast, if $\lamfac$ is chosen as an intermediate value, e.g.~$\lamfac = \Lambda/2$ or $\Lambda/4$, then the truncated system \eqref{TKdV} resolves scales that are both bigger and smaller than the characteristic value $\lam$.

@@

	Since the inverse temperature, $\theta$, is a key modeling parameter, it would be highly desirable to normalize the system such that the value of $\theta$ does not depend sensitively on the truncation number, $\Lambda$, as $\Lambda$ grows large. That way, $\theta$ can be interpreted as a real physical parameter that can be linked to the experiments and whose value does not depend sensitively on where one chooses to truncate the system. The one modeling parameter that is left to be set is $\lamfac$, which represents the number of characteristic wavelengths in the periodic domain. In what follows, we will determine reasonable constraints on $\lamfac$ that allow $\theta$ to be asymptotically independent of $\Lambda$.

@@

	Importantly, \eqref{HtwoExpect} shows that the expected value of $\Htwo$ grows like $\Lambda^2$, which appears to be problematic for obtaining independence as $\Lambda \to \infty$. However, $\Htwo$ enters $\Ham$ in product with the coefficient $C_2$, which itself scales as $C_2 \sim \lamfac^{-2}$. Hence, obtaining the desired asymptotic independence with respect to $\Lambda$ simply requires that $\lamfac$ grow proportionally to $\Lambda$, as was already argued on physical grounds in Section \ref{tKdVSec}. 
Thus, any of the choices $\lamfac = \Lambda$, $\Lambda/2$, or $\Lambda/4$, discussed in that section would be valid. In particular, if $\lamfac = \Lambda$, then the characteristic wavelength in experiments corresponds to the smallest resolved wavelength in the dynamical system. It is even more sensible to choose $\lamfac$ to be an intermediate value between 1 and $\Lambda$, so that some scales both larger than and smaller than the characteristic wavelength $\lam$ are resolved. As default, we will choose $\lamfac = \Lambda/2$, so that on a log-scale, the characteristic wavelength lies directly in the middle of the resolved wavelengths.
